---
title: "Assignment 9. Data visualization"
author: "YOUR NAME"
date: "11/11/2020"
output: html_document
---

```{r, message = FALSE, warning = FALSE}

library(tidyverse)
library(lubridate)
library(legislatoR)
library(RColorBrewer)
library(waffle)
library(ggthemes)
library(legislatoR)
library(dplyr)
library(forcats)
library(ggplot2)
library(hrbrthemes)
library(jtools)
library(stargazer)
library(ggstance)

```


<br>

## 1. Fetching data on members of the 115th United States Congress

The `legislatoR` package (https://github.com/saschagobel/legislatoR) provides access to the Comparative Legislators Database (CLD). The CLD includes political, sociodemographic, career, online presence, public attention, and visual information (organized in separate tables, very similar to a proper database structure) for over 45,000 contemporary and historical politicians from ten countries.

Install the package (either from CRAN or GitHub) and use it to compile the following data into one dataset:

a) The political data for the 115th session of the US House of Representatives
b) The data on daily user traffic on individual Wikipedia biographies (use it to compute the average number of daily page views per representative between January 3, 2017 and January 3, 2019 and match the variable to the dataset)
c) The information on the total number of sessions served by representative (compute it by counting the number of entries in the political table when grouped by representative).

```{r}
# YOUR CODE HERE


# a) 

# Get core data 
US_House <- get_core(legislature = "usa_house")

# Get political data  
US_Sessions <- get_political(legislature = "usa_house") 

# Filter for the 115th session
US_115 <- US_Sessions %>% filter(session == 115)




# b)

# Get wikipedia traffic data 
US_traffic <- get_traffic(legislature = "usa_house") 

# Filter for time frame and calculate average number of daily page views
US_daily <- US_traffic %>% 
  filter(date >= "2017-01-03" & date <= "2019-01-03") %>% 
  select(!date) %>% 
  group_by(pageid) %>%
  dplyr::summarize(Mean_DailyPageView = mean(traffic, na.rm=TRUE))




# c) 

US_Sessions_total <-  US_Sessions %>% group_by(pageid) %>% dplyr::summarize(Total_Sessions = n())

# Alternatively: 
#US_Sessions_total <-  US_Sessions %>% count(pageid) %>% rename(Total_Sessions = n)



# Finally, compiling all into one dataset:

Merged_Dataset <-  US_Sessions_total %>% 
  inner_join(US_daily, by = NULL) %>% 
  inner_join(US_115, by = NULL) 




```

<br> 

## 2. Exploring the dataset

Explore the dataset using visual means, following the guidelines of good visualization. Provide three different visualizations. One visualization is entirely up to you. The two others should give any two of the following:

a) gender or ethnicity distribution by party (Democrat/Republican; ignore the others)
b) age distribution by state in which the representative's district is located (limit to states with 10+ representatives)
c) top 10 representatives according to average daily page views
d) log mean page views vs. the number of sessions served

Transform the variables if needed (e.g., categorize continuous variables, pool residual categories into one, etc.).

```{r}


#a) ethnicity distribution by party (Democrat/Republican)

# Include gender, age, ethnicity data into the dataset 
Merged_Dataset_Big <-  Merged_Dataset %>% inner_join(US_House, by = NULL) 


# Democrats
# Filter for Party and count total number of representatives by ethnicity 

Prop_Ethicity_D <-  Merged_Dataset_Big %>% filter(party == "D") %>%  count(ethnicity) %>% rename(Total = n) %>% arrange(-Total) 
Labels_D <- c("White", "Black","Hispanic", "Asian", "Islander")


# Drawing a Waffle-Chart 

val_names <- sprintf("%s (%s)", Labels_D, scales::percent(round(Prop_Ethicity_D$Total/sum(Prop_Ethicity_D$Total), 5)))
names(Prop_Ethicity_D$Total) <- val_names

waffle::waffle(Prop_Ethicity_D$Total, rows=8, size=0.5, 
       title="Distribution of Ethnicites in the House: Democrats",
      xlab="1 Square = 1 Representative")


# Republicans
# Filter for Party and count total number of representatives by ethnicity 

Prop_Ethicity_R <-  Merged_Dataset_Big %>% filter(party == "R") %>%  count(ethnicity) %>% rename(Total = n) %>% arrange(-Total) 
Labels_R <- c("White", "Hispanic", "Black", "Native", "Islander")

# Drawing a Waffle-Chart 

val_names <- sprintf("%s (%s)", Labels_R, scales::percent(round(Prop_Ethicity_R$Total/sum(Prop_Ethicity_R$Total), 5)))
names(Prop_Ethicity_R$Total) <- val_names

waffle::waffle(Prop_Ethicity_R$Total, rows=8, size=0.5, 
       title ="Distribution of Ethnicites in the House: Republicans",
      xlab="1 Square = 1 Representative")



#c) top 10 representatives according to average daily page views

Merged_Dataset_Arranged <- Merged_Dataset_Big %>% arrange(-Mean_DailyPageView) %>% select(Mean_DailyPageView, name, party)
  
Merged_Dataset_Top10 <- Merged_Dataset_Arranged[1:10,] 



# Bar Chart 
Merged_Dataset_Top10  %>%
   mutate(name = fct_reorder(name, Mean_DailyPageView)) %>%
  ggplot(  aes(x= Mean_DailyPageView, y= name, fill = party)) +
    geom_bar(stat="identity", alpha=.6, width=.5) +
    xlab("Number of average Daily Wikipedia-Page Views") +
    ylab("Name of Representative") + 
    labs(fill = "Party") +
    theme_bw()

  

# Own Visualization: 

Merged_Dataset_Big %>% filter(party == "R"| party == "D") %>% 
  ggplot(aes(x= birth, y = Mean_DailyPageView, size = Total_Sessions, color= party)) + 
    geom_point(alpha=0.6) +
    scale_y_log10()+
    theme_ipsum() +
    xlab("Year of Birth") +
    ylab("Average number of daily page views") + 
    ggtitle("Relationship between Age, Nº of Sessions, Party and Views") +
    labs(color='Party') +
    labs(size='Nº of Sessions') 

# The graph shows  the connection between the age, the numbers of sessions served and the party-membership with the average number of daily page views on a log scale
# As we can see, older Republicans that served several sessions score the highest on the scale of average number of daily page views, but also several younger and less experienced democrats 





```


<br> 
2
## 3. Modeling page views

Finally, model the log number of mean page views as a function of the following variables: 

  - number of sessions served, 
  - party membership (Democrat/Republican/Independent)
  - key political position (a dummy which takes the value 1 if the representative is one of the following: speaker, majority/minority leader/whip)
  - age
  - gender
  - ethnicity (white/non-white)

A linear model is just fine. Present the results of your model in both a table and a coefficient plot!

```{r}


# Log of mean page views 
Merged_Dataset_Big$Views  <- log(Merged_Dataset_Big$Mean_DailyPageView)

# Transform ethnicity-variable into binary white/non-white variable 
Merged_Dataset_Big$ethnicity_new <- ifelse(Merged_Dataset_Big$ethnicity == "white", "white", "non-white")


# Sort party membership into 3 categories 
Merged_Dataset_Big$party_R <- ifelse(Merged_Dataset_Big$party == "R", 1 , 0)
Merged_Dataset_Big$party_D <- ifelse(Merged_Dataset_Big$party == "D", 1 , 0)
# As everything that is not R or D, i.e. "independent", is perfectly determined by R and D, it is automatically incorporated as baseline


# Age 

# Only one member of the 115th congress has already died (2018-03-16, 2 years ago); I do not account for that in this model as the effect of the actual age at death compared to the hypothetical age nowadays is neglectable 



Merged_Dataset_Big$YearBirth <- Merged_Dataset_Big$birth %>% 
                                          as.character() %>% 
                                           substr( 1, 4) %>% 
                                            as.double()
Merged_Dataset_Big$YearToday <- 2020

Merged_Dataset_Big <- Merged_Dataset_Big %>% mutate(Age = YearToday - YearBirth)



# Key political positions 
Merged_Dataset_Big$keyPosition <- ifelse(Merged_Dataset_Big$house_speaker == T | Merged_Dataset_Big$house_majority_leader == T | Merged_Dataset_Big$house_majority_whip == T | Merged_Dataset_Big$house_minority_leader == T | Merged_Dataset_Big$house_minority_whip == T, "1", "0")



# Linear Model 
linear_model <- lm(Views ~ sex + Age + keyPosition + ethnicity_new + Total_Sessions + party_R + party_D, data = Merged_Dataset_Big)

#CHANGE NAMES OF VARIABLES IN THE PLOTS!!
#TO SOMETHING ABOUT THE AGE VARIABLE!!!

own_labels =  c("Being Male", "Age", "Key Political Position", "Being White", "Total Nº Sessions", "Republicans", "Democrats")


stargazer(linear_model,
          title="Linear Model on Average Daily Page Views", 
          covariate.labels = own_labels, 
          type = "html",
          out = "Table_1.html",
          omit.stat=c("f", "ser"),
          style = "default")


# Coefficient Plots

Labels = c("Democrats"= "party_D", "Republicans" = "party_R", "Total Nº Sessions" = "Total_Sessions", "Being Male" = "sexmale", "Age" = "Age", "Key Political Position" = "keyPosition1", "Being White" = "ethnicity_newwhite")

jtools::plot_summs(linear_model , scale = TRUE,   plot.distributions = TRUE, coefs = Labels )

plot_summs(linear_model, scale = TRUE, inner_ci_level = .90, coefs = Labels)



```

